---
title: "HTML_Example"
author: "Jessica Young"
output:
  html_document:
    toc: yes
    toc_levels: 1
    toc_float: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
setwd('~/Desktop/Work Projects/intro_to_R/')

# the next 2 lines install the pacman package
# this allows you to use the p_load function which allows you to load in multiple packages in the same line 
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr, ggplot2, ggpubr)


# dplyr is useful for data manipulation
# ggplot2 is useful for creaitng plots
# ggpubr is a theme add-on to ggplot2 and makes plots paper-publish-ready
```

# RMarkdown Notation

In this setup line: `knitr::opts_chunk$set(echo = F, warning = F, message = F)`,

- `echo = F` makes sure that all your code chunks are not printed when you knit
- `warning = F` makes sure that any warnings your code produces is not printed when you knit
- `message = F` makes sure that any messages your code produces is not printed when you knit

These 3 options will make your final documents much neater and more professional looking!

Check out the header in the Rmd file, at the `output:` section, you'll see:

```{r, eval = F, echo = T}
output:
  html_document:
    toc: yes
    toc_levels: 1
    toc_float: yes
```

The first line after `output:` says to output an HTML document. The second says to include a table of contents. The third says to make the table of contents show only the highest level of bookmarks. And the final line says to let the table of contents float. If you open the HTML file on your browser, you'll see it floats on the left side when you scroll down the page.

Adding `{.tabset .tabset-fade .tabset-pills}` after headers produces buttons that allow you to hide any sub headers after that one unless you click on it. 

# cars Data Set{.tabset .tabset-fade .tabset-pills}

The cars dataset is available in base R.

## Summary

```{r}
summary(cars)
```

## Plots

Setting echo = T will print out the R code chunk into the final document.

```{r echo = T}

cars %>%
    ggplot(aes(x = speed, y = dist, col = "pink")) + 
    geom_point() +
    theme_pubr()

```

